% Describe a clear aim/purpose of the project. Make sure it is well motivated by the problem formulation
% You may divide the purpose into an overall purpose (your long term contribution in a  larger perspective) and more concrete goals (what you intend to do/deliver in order to
% reach the overall purpose).
% 8(19)
% Purpose/goal: What are you going to do, what do you want to achieve?

\section{Purpose}
The purpose of this report is to investigate the current situation and propose one or more alternative solutions for communication within the organization. The solution should be based on the background data collected while studying the problems as previously defined in section \ref{sec:problem-definition} (\textit{\nameref{sec:problem-definition}}). The solution should include a list of alternative services to use, with their respective pros and cons. It should also answer the following questions which are based on the problem definition.
\begin{enumerate}
\item Could RWHS improve their methods of working with digital services, for sharing, documenting and communicating information externally and internally by switching tools?
\item Would this alternative solution be able to provide the same quality of service at the same or only slightly greater cost than what is used today?
\item Would a new solution significantly speed up the learning rate and accessibility of information in the organization for all relevant parties?
\item Does the regulations regarding personal and sensitive data affect the choice of a future system?
\end{enumerate}
Furthermore the proposed alternative solutions has to fit the budgetary restrictions of RWHS, as well as comply with Swedish law (PUL/GDPR). The goal is that after the publication of this report, RWHS will be able to apply one of the proposed solutions to their organization. Upon successful implementation they should be able to observe increased efficiency because of a better digital solution. That would in turn hopefully ensure that the long term goals could be reached which includes fewer volunteers dropping of, and more landlords handled in a more efficient way. By optimizing the efficiency of RWHS, this project hopes to contribute to the project undertaken by them which in turn would contribute to  the same goals as the organization is working towards.







